Lifespan analysis

### 2023-07-10 stats/lifespan.Rmd
let analysis run, plot gp & cps together

```{r plot}
lifespan_plot <- lifespan_data %>% 
  group_by(subj_id, age, age_group) %>%
  summarise(mean = mean(click_dist_balloons, na.rm = TRUE)) %>% 
  ggplot(., aes(x = age, y = mean)) +
  geom_point(color = "darkgrey", alpha = 0.5) +
  geom_smooth(method = "loess", size = 1, se = T, color = "#006c66", fill = "#006c66") + 
  scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 5)) + 
  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 0.5)) + 
  labs(x = "Age in years", y = "Average imprecision in target widths")

lifespan_plot

ggsave("../figures/lifespan_plot.png", width = 8, height = 4, scale = 1.2)
saveRDS(lifespan_plot, "../saves/lifespan_plot.rds")
```

@@

conditional_effects(mcubic, ndraws = 200, spaghetti = TRUE) %>% 
  plot(points = T)

@@

# mdraws <- mdata %>%
#   add_predicted_draws(mgaussianprocess) %>% 
#   ungroup() %>% 
#   select(-c(.row, .chain, .iteration)) %>%
#   rename(draw = .draw, predicted_value = .prediction)
# 
# write.csv(mdraws, "../saves/lifespan_mdraws.csv", quote = F, row.names = F)
# saveRDS(mdraws, "../saves/lifespan_mdraws.rds")

@@

pred <- fitted(mgaussianprocess, newdata = nd, re_formula = NA) %>% as_tibble() %>% bind_cols(nd) 
```

@@

ibeast$trend$cp
```

@@

  # TODO: add lines where changepoints
  scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 5)) + 
  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 0.5)) +

>>>>

@@

conditional_effects(mcubic, ndraws = 200, spaghetti = TRUE) %>% 
  plot(points = T, yaxp = c(0,4,1))

@@

@@

pred <- fitted(mgaussianprocess, newdata = nd, re_formula = NA) %>% as_tibble() %>% bind_cols(nd)

write.csv(pred, "../saves/lifespan_mgpdraws.csv", quote = F, row.names = F)
saveRDS(pred, "../saves/lifespan_mgpdraws.rds")
```

@@

# how many changepoints?
ibeast$trend$ncp_median

# location of changepoints
ibeast$trend$cp

# pull out all relevant change points
cps <- tibble(
          cp = ibeast$trend$cp[1:ibeast$trend$ncp_median], 
          lowerCrI = ibeast$trend$cpCI[1:ibeast$trend$ncp_median,1], 
          upperCrI = ibeast$trend$cpCI[1:ibeast$trend$ncp_median,2]
       )

saveRDS(ibeast, "../saves/lifespan_ibeast.rds")

write.csv(cps, "../saves/lifespan_ibeast_cps.csv", quote = F, row.names = F)
saveRDS(cps, "../saves/lifespan_ibeast_cps.rds")
```

@@

  geom_vline(xintercept = cps$cp, linetype = "dashed", alpha = 0.75, size = 1) +
  # geom_vline(xintercept = cps$lowerCrI, linetype = "dotted", alpha = 0.5, size = 1) +
  # geom_vline(xintercept = cps$upperCrI, linetype = "dotted", alpha = 0.5, size = 1) +

  scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 5)) + 
  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 0.5)) +

  labs(x = "Age in years", y = "Average imprecision in target width")

# ZOOM IN
ggplot() +

  geom_vline(xintercept = cps$cp, linetype = "dashed", alpha = 0.75, size = 1) +

  scale_x_continuous(limits = c(0, 80), breaks = seq(0, 80, 0.5)) + 
  scale_y_continuous(limits = c(0, 4), breaks = seq(0, 4, 0.5)) +

  coord_cartesian(xlim = c(3, 10), ) +
